Theory about Normal Basis on $F(2^k)$

### 2016-12-24 dissertation/submission/unsat.tex
dissertation after defense update 2

\begin{figure}[H]
\centering{
\includegraphics[scale=0.3]{newfig/fig_SAT.eps}
\caption{An example of Boolean satisfiability problem on circuits}
\label{fig:SAT}}
\end{figure}

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|c|} 
\hline
 Boolean operator & Function over $\Fkk$ \\
\hline
\hline
 $a\land b$ & $a\cdot b$ \\
\hline
 $a\oplus b$ & $a+b$ \\
\hline
 $\bar{a}$ & $1+a$ \\
\hline
 $a\lor b$ & $a+b+a\cdot b$\\
\hline
\end{tabular}
\caption{Mapping Boolean operators to functions over $\Fkk$}
\label{tab:booltof4}  
\end{table}

@@

\begin{figure}[hbt]
\centering{
\includegraphics[width=5.5in]{newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
Assume that we are given a sequential circuit with $n$ latches as shown in Figure \ref{fig:refine}(a). 
This circuit can be modeled as a Mealy machine $M$ and the states $s$ can be explicitly encoded by bit-level latch variables 
$l_1,\dots,l_n$. Algorithm \ref{alg:absrefine} describes an approach to check if machine $M$ violates property $p$.
This algorithm relies on $k$-BMC technique, which works on the basis of CNF-SAT solving.
The $k$-BMC represents the initial states $I$, the transition relation $T$ and property $p$ as CNF formulas.

@@

\vspace{0.1in}
We compute its GB using Buchberger's algorithm with lexicographic term ordering $a>b>x>y>z$.
Since this problem is UNSAT, we will stop when ``1" is added to GB.
\begin{enumerate}[{1)}]
\item First we compute $Spoly(f_1,f_2)\xrightarrow{F}_{+} r_1$, remainder $r_1$ equals to $a$;
\item Update $F=F\cup r_1$;
\item Next we compute $Spoly(f_1,f_3)\xrightarrow{F}_{+} r_2$, remainder $r_2$ equals to $b$;
\item Update $F=F\cup r_2$;
\item We can use a directed acyclic graph (DAG) to represent the process to get $r_1,r_2$, as Figure \ref{fig:UNSAT}(a) shows;
\item Then we compute $Spoly(f_1,f_4) = s_3= a+b+1$, obviously $a+b+1$ can be reduced (multivariate divided) by
$r_1$ , the intermediate remainder $r_3 = b+1$. It can be immediately divided by $r_2$, and the remainder is ``1", we
terminate the Buchberger's algorithm;
\item We draw a DAG depicting the process through which we obtain remainder ``1" as shown in Figure \ref{fig:UNSAT}(b). 
From leaf ``1" we backtrace the graph to roots $f_1,f_2,f_3,f_4$. They constitute an UNSAT core for this problem
as these polynomials are the ``causes" of unsatisfiability of original set of polynomials.
\end{enumerate}
\end{Example}
\begin{figure}[hbt]
\centering{
\includegraphics[width=\textwidth]{newfig/UNSAT.eps}
\caption{DAG representing $Spoly$ computations and multivariate divisions}
\label{fig:UNSAT}}
\end{figure}

@@

\begin{figure}[hbt]
\centering
\includegraphics[width=4.5in]{newfig/refutation_tree.eps}
\caption{Generating refutation trees to record UNSAT cores}
\label{fig:refute}
\end{figure}

@@

After the first iteration of the GB-core algorithm, the core is
identified as $\{f_1, f_2,f_3,f_4\}$, and we obtain a
refutation tree as shown in Figure \ref{fig:refine}(a).  
\begin{figure}[hbt]
\centering
\includegraphics[width=\textwidth]{newfig/core_refine.eps}
\caption{Refutation trees of core refinement example}
\label{fig:refine}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/s27.pdf}
\caption{Gate-level Schematic of Example Circuit}
\label{fig:s27}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{newfig/s27_stg.pdf}
\caption{State transition graph of example circuit}
\label{fig:s27_stg}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{newfig/s27_stg_refined.pdf}
\caption{State transition graph of abstracted machine}
\label{fig:s27_stg_refined}}
\end{figure}

@@

%\vspace{-0.1in}
\begin{table}[htb]
\centering
\caption{Results of running benchmarks using our tool. 
\small{Asterisk($^*$) denotes that the benchmark was not translated from CNF.} 
Our tool is composed by 3 parts: part I runs a single GB-core algorithm,
part II applies the iterative refinement heuristic to run the GB-core algorithm
iteratively, part III applies the syzygy heuristic.}
{\small 
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{3}{2.2cm}{\centering Benchmark} 
& \multirow{3}{0.9cm}{\centering \# Polys} 
& \multirow{3}{0.8cm}{\centering \# MUS} 
& \multicolumn{3}{c|}{\multirow{2}{1.8cm}{\centering Size of core}}
 & \multirow{3}{1.6cm}{\centering \# GB-core iterations}
 & \multicolumn{3}{c|}{\multirow{2}{2.0cm}{\centering Runtime (sec)}}
 & \multirow{3}{1.8cm}{\centering Runtime of PicoMUS (sec)} \\
  & & &\multicolumn{3}{c|}{}& &\multicolumn{3}{c|}{}& \\
  \cline{4-6} \cline{8-10}
    & & & I & II & III & & I & II & III & \\
\hline
\hline
$5\times 5$ SMPO & 240  & 137  & 169 & 137 & 137  & 8  & 1222 & 1938 & 1698 & $<0.1$\\
$4\times 4$ SMPO$^*$ & 84  & 21  & 21 & 21 & 21 & 1  & 125 & 0.3 & 29  & - \\
$3\times 3$ SMPO$^*$ & 45  & 15  & 15 & 15 & 15  & 1  & 6.6 & 0.2 & 5.7 & - \\
$3 \times 3$ SMPO & 17 & 2 & 2 &2 & 2 & 1 & 0.07 & 0.01 & 0.01  & $<0.1$  \\
$4 \times 4$ MasVMont$^*$ & 148 & 83 & 83 & 83 & 83 & 1 & 23 & 139 & 12 & - \\
$3 \times 3$ MasVMont$^*$ & 84 & 53 & 53 & 53 & 53  & 1 & 4.3 & 4.6 & 0.9  & - \\
$2 \times 2$ MasVMont & 27 & 23 & 24 & 23 & 23 & 2 & 1.3 & 1.0 & 80  & $<0.1$ \\
$5\times 5$ RH$^*$ & 142  & 34  & 48 & 35 & 35  & 4  & 997 & 1.0 & 80 & - \\
$4\times 4$ RH$^*$ & 104  & 35  & 43 & 36 & 36  & 3  & 96 & 5.7 & 0.6 & -\\
$3\times 3$ RH$^*$ & 50  & 20  & 20 & 20 & 20  & 1  &2.9 & 3.5 & 10  & -\\
aim-100 & 79 & 22 & 22 & 22 & 22 & 1  & 43 & 0.7 & 0.2 & $<0.1$\\
cocktail & 135 & 4 & 6 & 4 & 4 & 2 & 51 & 0.01 & 0.01  & $<0.1$ \\
subset-1 & 100 & 6 & 6 & 6 & 6 & 1 & 2.4 & 0.01 & 0.01 & $<0.1$ \\
subset-2 & 141 & 19 & 37 & 23 & 21 & 2 & 12 & 1.6 & 1.1 & $<0.1$  \\
subset-3 & 118 & 16 & 13 & 12 & 11 & 2 & 8.6 & 0.2 & 0.07 & $<0.1$ \\
phole4 & 104 & 10 & 16 & 16 & 10 & 1 & 4.3 & 0.2 & 0.5 &  $<0.1$\\
phole5 & 169 & 19 & 30 & 25 & 19 & 3 & 12 & 3.2 & 2.7 & $<0.1$ \\
\hline
\end{tabular}
}
\label{tab:result}  
\end{table}

>>>>

\begin{figure}[H]
\centering{
\includegraphics[scale=0.3]{newfig/fig_SAT.eps}}
\caption{An example of Boolean satisfiability problem on circuits.}
\label{fig:SAT}
\end{figure}

@@

\begin{table}[h]
\caption{Mapping Boolean operators to functions over $\Fkk$}
\centering
\begin{tabular}{|c|c|} 
\hline
 Boolean operator & Function over $\Fkk$ \\
\hline
\hline
 $a\land b$ & $a\cdot b$ \\
\hline
 $a\oplus b$ & $a+b$ \\
\hline
 $\bar{a}$ & $1+a$ \\
\hline
 $a\lor b$ & $a+b+a\cdot b$\\
\hline
\end{tabular}
\label{tab:booltof4}  
\end{table}

@@

\begin{figure}[h]
\centering{
\includegraphics[width=5.5in]{newfig/refine.eps}}
\caption{Abstraction by reducing latches.}
\label{fig:refine}
\end{figure}
Assume that we are given a sequential circuit with $n$ latches as shown in Figure \ref{fig:refine}(a). 
This circuit can be modeled as a Mealy machine $M$ and the states $s$ can be explicitly encoded by bit-level latch variables 
$l_1,\dots,l_n$. Algorithm \ref{alg:absrefine} describes an approach to check if machine $M$ violates property $p$.
This algorithm relies on $k$-BMC technique, which works on the basis of CNF-SAT solving.
The $k$-BMC represents the initial states $I$, the transition relation $T$ and property $p$ as CNF formulas.

@@

\vspace{0.1in}
We compute its GB using Buchberger's algorithm with lexicographic term ordering $a>b>x>y>z$.
Since this problem is UNSAT, we will stop when ``1" is added to GB.
\begin{enumerate}[{1)}]
\item First we compute $Spoly(f_1,f_2)\xrightarrow{F}_{+} r_1$, remainder $r_1$ equals to $a$;
\item Update $F=F\cup r_1$;
\item Next we compute $Spoly(f_1,f_3)\xrightarrow{F}_{+} r_2$, remainder $r_2$ equals to $b$;
\item Update $F=F\cup r_2$;
\item We can use a directed acyclic graph (DAG) to represent the process to get $r_1,r_2$, as Figure \ref{fig:UNSAT}(a) shows;
\item Then we compute $Spoly(f_1,f_4) = s_3= a+b+1$, obviously $a+b+1$ can be reduced (multivariate divided) by
$r_1$ , the intermediate remainder $r_3 = b+1$. It can be immediately divided by $r_2$, and the remainder is ``1", we
terminate the Buchberger's algorithm;
\item We draw a DAG depicting the process through which we obtain remainder ``1" as shown in Figure \ref{fig:UNSAT}(b). 
From leaf ``1" we backtrace the graph to roots $f_1,f_2,f_3,f_4$. They constitute an UNSAT core for this problem
as these polynomials are the ``causes" of unsatisfiability of original set of polynomials.
\end{enumerate}
\end{Example}
\begin{figure}[h]
\centering{
\includegraphics[width=\textwidth]{newfig/UNSAT.eps}
\caption{DAG representing $Spoly$ computations and multivariate divisions.}}
\label{fig:UNSAT}
\end{figure}

@@

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/refutation_tree.eps}}
\caption{Generating refutation trees to record UNSAT cores.}
\label{fig:refute}
\end{figure}

@@

After the first iteration of the GB-core algorithm, the core is
identified as $\{f_1, f_2,f_3,f_4\}$, and we obtain a
refutation tree as shown in Figure \ref{fig:refine}(a).  
\begin{figure}[h]
\centering{
\includegraphics[width=\textwidth]{newfig/core_refine.eps}}
\caption{Refutation trees of core refinement example.}
\label{fig:refine}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/s27.eps}
\caption{Gate-level schematic of the example circuit.}}
\label{fig:s27}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{newfig/s27_stg.pdf}}
\caption{State transition graph of example circuit.}
\label{fig:s27_stg}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=4.5in]{newfig/s27_stg_refined.pdf}}
\caption{State transition graph of abstracted machine.}
\label{fig:s27_stg_refined}
\end{figure}

@@

%\vspace{-0.1in}
\begin{table}[htb]
\centering
\caption{Results of running benchmarks using our tool. 
\small{Asterisk($^*$) denotes that the benchmark was not translated from CNF.} 
Our tool is composed by 3 parts: part I runs a single GB-core algorithm,
part II applies the iterative refinement heuristic to run the GB-core algorithm
iteratively, part III applies the syzygy heuristic.}
{\small 
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{3}{1.8cm}{\centering Benchmark} 
& \multirow{3}{0.7cm}{\centering \# Polys} 
& \multirow{3}{0.7cm}{\centering \# MUS} 
& \multicolumn{3}{c|}{\multirow{2}{1.5cm}{\centering Size of core}}
 & \multirow{3}{1.3cm}{\centering \# GB-core iterations}
 & \multicolumn{3}{c|}{\multirow{2}{1.8cm}{\centering Runtime (sec)}}
 & \multirow{3}{1.6cm}{\centering Runtime of PicoMUS (sec)} \\
  & & &\multicolumn{3}{c|}{}& &\multicolumn{3}{c|}{}& \\
  \cline{4-6} \cline{8-10}
    & & & I & II & III & & I & II & III & \\
\hline
\hline
$5\times 5$ SMPO & 240  & 137  & 169 & 137 & 137  & 8  & 1222 & 1938 & 1698 & $<0.1$\\
$4\times 4$ SMPO$^*$ & 84  & 21  & 21 & 21 & 21 & 1  & 125 & 0.3 & 29  & - \\
$3\times 3$ SMPO$^*$ & 45  & 15  & 15 & 15 & 15  & 1  & 6.6 & 0.2 & 5.7 & - \\
$3 \times 3$ SMPO & 17 & 2 & 2 &2 & 2 & 1 & 0.07 & 0.01 & 0.01  & $<0.1$  \\
$4 \times 4$ MasVMont$^*$ & 148 & 83 & 83 & 83 & 83 & 1 & 23 & 139 & 12 & - \\
$3 \times 3$ MasVMont$^*$ & 84 & 53 & 53 & 53 & 53  & 1 & 4.3 & 4.6 & 0.9  & - \\
$2 \times 2$ MasVMont & 27 & 23 & 24 & 23 & 23 & 2 & 1.3 & 1.0 & 80  & $<0.1$ \\
$5\times 5$ RH$^*$ & 142  & 34  & 48 & 35 & 35  & 4  & 997 & 1.0 & 80 & - \\
$4\times 4$ RH$^*$ & 104  & 35  & 43 & 36 & 36  & 3  & 96 & 5.7 & 0.6 & -\\
$3\times 3$ RH$^*$ & 50  & 20  & 20 & 20 & 20  & 1  &2.9 & 3.5 & 10  & -\\
aim-100 & 79 & 22 & 22 & 22 & 22 & 1  & 43 & 0.7 & 0.2 & $<0.1$\\
cocktail & 135 & 4 & 6 & 4 & 4 & 2 & 51 & 0.01 & 0.01  & $<0.1$ \\
subset-1 & 100 & 6 & 6 & 6 & 6 & 1 & 2.4 & 0.01 & 0.01 & $<0.1$ \\
subset-2 & 141 & 19 & 37 & 23 & 21 & 2 & 12 & 1.6 & 1.1 & $<0.1$  \\
subset-3 & 118 & 16 & 13 & 12 & 11 & 2 & 8.6 & 0.2 & 0.07 & $<0.1$ \\
phole4 & 104 & 10 & 16 & 16 & 10 & 1 & 4.3 & 0.2 & 0.5 &  $<0.1$\\
phole5 & 169 & 19 & 30 & 25 & 19 & 3 & 12 & 3.2 & 2.7 & $<0.1$ \\
\hline
\end{tabular}
}
\label{tab:result}  
\end{table}
